---
title: "Interactive Visualizations"
output: 
    html_document:
        toc: TRUE
        toc_float: TRUE
---

<br>

Here are some more interactive visualizations :)

<br>

```{r setup, message=FALSE, echo=FALSE, warning=FALSE}

library(data.table)
library(tidyverse)
library(dplyr)
library(plotly)
library(DT)
library(knitr)
library(leaflet)

# Initialize code chunk options
opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  eval=TRUE,
  echo = TRUE,
  cache = FALSE,
  fig.width = 7, 
  fig.align = 'center',
  fig.asp = 0.618,
  out.width = "700px",
  class.source = "code-r")
```

```{css, echo = FALSE}
.code-r { /* Code block */
  font-size: 15px;
}

.code-r-small { /* Code block */
  font-size: 10px;
}
```

```{r load_data, message=FALSE, echo=FALSE, warning=FALSE}
data = read.csv("data/delay_weather.csv")
data_delay = read.csv("data/Airline_Delay_Cause.csv")
closest_station = data

data = data %>% mutate(pct_cancel = arr_cancelled/arr_flights,
                 pct_delay= arr_delayed/arr_flights)
p1 <- data %>% 
  plot_ly(x = ~arr_delayed, y = ~arr_cancelled,
          type = 'scatter', mode = 'markers', color = ~region_name,
          size = ~arr_delay_time, sizes = c(5, 70), marker = list(sizemode='diameter', opacity=0.5),
          hoverinfo = 'text',
          text = ~paste( paste(region_name, ":", sep=""), paste(" arrival flights: ", arr_flights, sep="") , paste(" number of arrival cancelled: ", arr_cancelled, sep=""), paste(" number of arrival delayed: ", arr_delayed, sep=""), sep = "<br>")) %>%
  layout(title = "Number of Arrival Delayed vs Cancelled",
                  yaxis = list(title = "Number of Arrival Cancelled"), xaxis = list(title = "Number of Arrival Delayed"),
         hovermode = "compare")
         

delay_pal = colorNumeric(c('lightblue', 'pink','red', 'darkred'),
                      domain = closest_station$pct_delay)
p2 = leaflet(closest_station) %>%
  addProviderTiles('OpenStreetMap') %>%
  addCircles(lat = ~latitude_deg, lng = ~longitude_deg, color = ~delay_pal(pct_delay),
             label = ~paste0(round(pct_delay, 3), 'delay'),
             opacity = 1,
             fillOpacity = 1,
             radius = 500) %>%
#  addMarkers(lat = ~lat, lng = ~lon,
#             label = ~paste0(round(rh,2), 'rh'),
#            data = top10) %>%
addLegend('bottomleft', pal = delay_pal, values = closest_station$pct_delay,
          title = "proportion of delay (%)", opacity = 1)

delay_pal = colorNumeric(c('lightblue', 'pink','red', 'darkred'),
                      domain = closest_station$pct_cancel)
p3 = leaflet(closest_station) %>%
  addProviderTiles('OpenStreetMap') %>%
  addCircles(lat = ~latitude_deg, lng = ~longitude_deg, color = ~delay_pal(pct_cancel),
             label = ~paste0(round(pct_cancel, 3), 'cancel'),
             opacity = 1,
             fillOpacity = 1,
             radius = 500) %>%
#  addMarkers(lat = ~lat, lng = ~lon,
#             label = ~paste0(round(rh,2), 'rh'),
#            data = top10) %>%
addLegend('bottomleft', pal = delay_pal, values = closest_station$pct_cancel,
          title = "proportion of cancel (%)", opacity = 1)

delay_pal = colorNumeric(c( 'darkgreen','lightgreen','lightblue', 'darkblue'),
                      domain = closest_station$wind.sp)
p4 = leaflet(closest_station) %>%
  addProviderTiles('OpenStreetMap') %>%
  addCircles(lat = ~latitude_deg, lng = ~longitude_deg, color = ~delay_pal(wind.sp),
             label = ~paste0(round(wind.sp, 3), 'delay'),
             opacity = 1,
             fillOpacity = 1,
             radius = 500) %>%
#  addMarkers(lat = ~lat, lng = ~lon,
#             label = ~paste0(round(rh,2), 'rh'),
#            data = top10) %>%
addLegend('bottomleft', pal = delay_pal, values = closest_station$wind.sp,
          title = "wind speed", opacity = 1)
```

<p style="font-family: times, serif; font-size:12pt">
This map shows the proportion of delays of the airports in the US. Where blue indicates low proportion of delay and red indicates high proportion of delay. We can see that there are a higher proportion of delays in the coastal region and eastern part of US.
</p>



## Number of Arrival Delayed vs Cancelled
```{r, echo=FALSE}
p1
```
This plot will have the number of delayed flights on the x-axis and the number of cancelled flights on the y-axis. Each point on the scatter plot will represent a specific airport, with the color of the point indicating the region. The size of each point will be determined by the duration of the delay time. We also adds text to each point that will appear when hovering over the point. The text will display information about the region, including the total number of arrival flights, the number of cancelled arrivals, and the number of delayed arrivals.

## Map for Percentage of Flight Delays

```{r, echo=FALSE}
p2
```
<p style="font-family: times, serif; font-size:12pt">
This map shows the proportion of delayed flights of the airports in the US. Where blue indicates low proportion of cancels and red indicates high proportion of cancels. We can see that there are a higher proportion of cancelled flights in the coastal region and eastern part of US. This is very similar with the flight delay observations.
</p>




## Map for Percentage of Flight Cancel

```{r, echo=FALSE}
p3
```
<p style="font-family: times, serif; font-size:12pt">
This map shows the proportion of cancelled flights of the airports in the US. Where blue indicates low proportion of cancels and red indicates high proportion of cancels. We can see that there are a higher proportion of cancelled flights in the coastal region and eastern part of US. This is very similar with the flight delay observations.
</p>

## Map for Wind Speed

```{r, echo=FALSE}
p4
```
<p style="font-family: times, serif; font-size:12pt">
This map gives us an overview of wind speed in the US. Where blue indicates high wind speed and green indicates low wind speed. We can see that the wind is stronger in middle region and coastal region. Some regions overlap with the regions with high flight delay and cancel rates.
</p>

